Methods for Analyzing Models of\\ Rod-Shaped Bacteria

### 2025-09-29 paper/main.tex
add points for future ideas
remove from description
adjust formatting
adjust text to new optimization setup; include figure for amir

\begin{figure}
    \centering
    \begin{tikzonimage}[width=0.32\textwidth]
        {docs/source/_static/fitting-methods/extract_positions-004000.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{A}};
    \end{tikzonimage}
    \begin{tikzonimage}[width=0.32\textwidth]
        {docs/source/_static/fitting-methods/extract_positions-006000.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{B}};
    \end{tikzonimage}
    \begin{tikzonimage}[width=0.32\textwidth]
        {docs/source/_static/fitting-methods/extract_positions-008000.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{C}};
    \end{tikzonimage}
    \begin{tikzonimage}[width=0.5\textwidth]
        {docs/source/_static/fitting-methods/displacement-calculations.png}%
        \node at (0.03, 0.99)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{D}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.5\textwidth]
        {docs/source/_static/fitting-methods/displacement-distribution.png}
        \node at (0.03, 0.99)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{E}};
    \end{tikzonimage}
    \caption{
        Subfigures (A-C) show rendered masks of a simulation where the extracted positions have been
        drawn within the individual agents.
        Subfigure (D) displayes the average rod length of the exact and extracted data.
        The light blue region is the mean distance between vertices of extracted and exact
        positions which captures the inherent uncertainty of our method.
        Subfigure (E) displays all of these distances on a logarithmic scale.
        The colorscale represents earlier (darker) and later (brighter) temporal states of our
        simulation.
        Overall, this plot shows a widening of the distance distributions for increasing simulation
        times.
    }
    \label{fig:benchmarking-extraction-algorithm}
\end{figure}

@@

\begin{figure}
    \centering
    \begin{minipage}{0.33\textwidth}
        \begin{tikzonimage}[width=\textwidth]
            {figures/amir-elastic-000032-wider.png}%
            \node at (0.01, 0.01+17pt)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{A}};
        \end{tikzonimage}%
    \end{minipage}%
    \begin{minipage}{0.66\textwidth}
        \begin{tikzonimage}[width=0.33\textwidth]
            {figures/crm_amir/profiles-full/fit-comparison.pdf}%
            \node at (0.15, 0.86)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{B}};
        \end{tikzonimage}%
        \begin{tikzonimage}[width=0.33\textwidth]
            {figures/crm_amir/profiles-full/drag force.pdf}%
            \node at (0.15, 0.86)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{C}};
        \end{tikzonimage}%
        \begin{tikzonimage}[width=0.33\textwidth]
            {figures/crm_amir/profiles-full/growth rate.pdf}%
            \node at (0.15, 0.86)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{D}};
        \end{tikzonimage}\\
        \begin{tikzonimage}[width=0.33\textwidth]
            {figures/crm_amir/profiles-full/rod rigidity.pdf}%
            \node at (0.15, 0.86)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{E}};
        \end{tikzonimage}%
        \begin{tikzonimage}[width=0.33\textwidth]
            {figures/crm_amir/profiles-full/spring tension.pdf}%
            \node at (0.15, 0.86)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{F}};
        \end{tikzonimage}%
        \begin{tikzonimage}[width=0.33\textwidth]
            {figures/crm_amir/profiles-full/damping.pdf}%
            \node at (0.15, 0.86)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{G}};
        \end{tikzonimage}%
    \end{minipage}
    \caption{
        Subfigure (A) shows a snapshot of the experiments performed by \cite{Amir2014_2}.
        Division of the bacteria is inhibited and they are trapped within a mother machine such that
        a controlled flow can be exerted on them.
        (B) A comparison of the initial and bent state show good visual agreement of our prediction
        with the experimental data.
        Subfigures (C-G) show likelihood profiles for the individual parameters.
    }
    \label{fig:amir-bending-simulation}
\end{figure}

@@

To show the usefulness of our previously developed methods (see
section~\ref{section:parameter-estimation}), we will use them to estimate the parameters of a
sequence of microscopic images of growing \texttt{E.Coli}.
The data we use~\cite{https://doi.org/10.3203/iwf/k-129} (see
section~\ref{section:data-code-availability}) has been automatically segmented with the
omnipose~\cite{Cutler2022} algorithm which provides us with the necessary cell masks.

% --------------------------------------------------------------------------------------------------
\subsection{Individual Treatment}
We have already suspected (see table~\ref{table:simulation-aspects}) that in order to properly
estimate parameters of our system, we need to treat every cell-agent individually, thus assigning
parameters on a single-cell level.
This would mean to increase the total number of parameters that need to be sampled within an
optimization routine.
Given $N_c$ cells and $N_p$ parameters per cell and $N_u$ individual parameters (where
$N_u\leq N_p$), the total amount of parameters is

@@

It is clear, that we should avoid to needlessly assign every parameter individually since the volume
of the space that needs to be sampled, scales exponentially with the dimension ie. the number of
parameters.
However, we will now present data that indicate that an individual treatment is in fact necessary.
Figure~\ref{fig:estimated-growth-rates} shows the rod-lengths of individual bacteria which have been
calculated from the extracted positions.
We fit a delayed exponential function to them which is defined by

@@

% --------------------------------------------------------------------------------------------------
\subsection{Without Division}
For now, we will focus on a time-interval which does not contain any division events and at which
the initial lag-phase of our bacteria os already passed.
By doing so, we can utilize the simpler and more performant position comparison scheme for our loss
function.
Furthermore, we need not to estimate the lag-time parameters which improves performance of our
optimization algorithm.
For this dataset, we assumed that all parameters which specify the interaction potential are
identical across all agents but growth rates of the cells are individual.

We chose to optimize for the damping of agents' movement within the medium, 3 interaction parameters
of the Mie potential $n,m,V_0$ a single radius for all agents and growth rates which were chosen
individually for each cell.
We removed any stochastic motion contributions by setting $D=0$.
This leads to a total of $5+1\times 6=11$ variable parameters.
As highlighted before, in order to model non-flexible rods, we set the rigidity and spring tension
of the rod to a high, fixed value.
To estimate these parameters we used the differential evolution~\cite{Storn1997} global optimization
algorithm which was initially seeded with a sample generated by the latin-hypercube~\cite{McKay1979}
method.
Finally, we performed a local minimization using the L-BFGS-B algorithm~\cite{Liu1989}.

Figure~\ref{fig:parameter-estimates-single-step} shows profile-likelihoods for each optimized
parameter with respect to the optimization results described before.
We can see that all parameters can be estimated by our optimization approach and that no
non-identifiability~\cite{Raue2009} is present.

@@

In the next step, we extend our previously used time-series with additional images, which include
cell division events which means that we now have to use the imaing-based comparison algorithm (see
section~\ref{section:parameter-estimation}).
A practical problem in extending the time series is that the segmentation algorithm was not able to
properly segment the individual bacteria around the division event which meant that we had to omit
parts of the snapshots, leaving us with only incomplete data.

Since we have already optimized said system, we can reduce the computational demand by choosing the
parameters which were obtained by our previous attempts and extend them with the parameters that the
daughter cells will carry.
In addition to assigning growth rates individually, but we also need to consider division lengths at
which the bacteria split.
Since our simulation involves the division of 4 cells into 8 new ones, in principle, this would lead
us to a total of $8$ new growth rates and $4$ division lengths.
But to decrease the size of the parameter space, we assume that the growth rates of the daughter
cells are identical between every sibling, leaving us at only $4$ new growth rates and a total of
$8$ parameters.
Future approaches should aim to loosen this assumption, allowing to optimize every new growth rate.
To optimize this system, we again used the same optimization approach by seed with samples generated
by latin-hypercube~\cite{McKay1979}, then applying the differential evolution
algorithm~\cite{Storn1997} and finally a local minimization via L-BFGS-B~\cite{Liu1989}.
We used the value $0.5$ for the parent penalty, which aims to provide a smooth transition between
not accounting for them and assigning full weighting to this difference.
Figure~\ref{fig:celldiffs-progression-with-division} shows the difference between the cell mask as
given by the data and the cell mask predicted by the best fit of our model.

We can again calculate likelihood profiles for every optimized parameter.
The results displayed in Figure~\ref{fig:likelihood-profiles-comparison-with-division} show that the
values for the division lengths exhibit a decrease in steepness of the curve towards the left side
of the estimated parameter.
This can be attributed to the missing images which were not able to be segmented in our time series.
It can be argued that this leads to a non-identifiability for the first division length while the
remaining parameters are still identifiable although the effect is also notable.
These results highlight a reassuring finding, namely that the method of profile-likelihood is able
to properly display this lack of data.
It therefore further underlines the accuracy of our methods.
In comparison, the growth rates of the daughter cells display larger variations within their
likelihood profiles.
\textbf{TODO finish this; need more results for otimization of all daughter growth rates as well}

It has to be noted that this approach is computationally much more expensive compared to the simpler
position-comparison algorithm.
There are 4 main steps which are executed within any single optimization iteration that contribute
to the total wall time.
These steps are prediction via the computational model ($15.63(21)\%$), mask adjustment of the data
masks ($14.49(19)\%$), mask rendering for the numerical results ($69.2(1.4)\%$) and finally
comparison of the masks ($0.68(5)\%$) (see section \ref{section:supplement-performance}).
The masks which are provided by the data need to be adjusted such that the identifiers of the cells
which are directly related to the chosen colors match with the ones used within the masks provided
by the data.
It is clear that the generation of masks from the numerical results takes up the majority of the
work.
In addition, the step of mask adjustment would not have been required within the position-comparison
algorithm.
Combining these two values, the position-comparison algorithm is $\approx 6.13(8)$ times faster.

@@

\begin{itemize}
    \item Model does not capture every aspect of rod-shaped bacteria. Needs to extended (see our
        review).
    \begin{enumerate}
        \item polar interactions
        \item differentiation for van Gogh bundles; surfactin-producing, matrix-producing cells.
        \item Proper friction; this might have a huge implication on the estimation of
            parameters~\cite{Grant2014}.
            This paper has already implemented this~\cite{Doumic2020}.
            We can build on top of that.
        \item Extracellular Reactions~\cite{Li2025}
        \item see supplement for full list \ref{table:simulation-aspects-supplement}
    \end{enumerate}
    \item Data Extraction: Skeletonization Algorithm ultimately not good enough for some scenarios
        (i.e. overlapping of cells, endpoints can sometimes be "too short")
    \begin{itemize}
        \item Possibly use AI for new algorithm
    \end{itemize}
    \item Image generation; Produce high-quality near-realistic microscopic images with cell-masks
        from scratch with mechanistic model; train cell-segmentation and more importantly
        cell-tracking algorithms with that.
\end{itemize}

@@

@@

>>>>

\begin{figure}
    \centering
    \begin{tikzonimage}[width=0.32\textwidth]
        {docs/source/_static/fitting-methods/extract_positions-004000.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{A}};
    \end{tikzonimage}
    \begin{tikzonimage}[width=0.32\textwidth]
        {docs/source/_static/fitting-methods/extract_positions-006000.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{B}};
    \end{tikzonimage}
    \begin{tikzonimage}[width=0.32\textwidth]
        {docs/source/_static/fitting-methods/extract_positions-008000.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{C}};
    \end{tikzonimage}
    \begin{tikzonimage}[width=0.5\textwidth]
        {docs/source/_static/fitting-methods/displacement-calculations.png}%
        \node at (0.03, 0.99)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{D}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.5\textwidth]
        {docs/source/_static/fitting-methods/displacement-distribution.png}
        \node at (0.03, 0.99)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{E}};
    \end{tikzonimage}
    \caption{
        Subfigures (A-C) show rendered masks of a simulation where the extracted positions have been
        drawn within the individual agents.
        Subfigure (D) displayes the average rod length of the exact and extracted data.
        The light blue region is the mean distance between vertices of extracted and exact
        positions which captures the inherent uncertainty of our method.
        Subfigure (E) displays all of these distances on a logarithmic scale.
        The colorscale represents earlier (darker) and later (brighter) temporal states of our
        simulation.
    }
    \label{fig:benchmarking-extraction-algorithm}
\end{figure}

@@

\begin{figure}
    \centering
    \begin{minipage}{0.38\textwidth}
        \begin{tikzonimage}[width=\textwidth]
            {figures/amir-elastic-000032-wider.png}%
            \node at (0.01, 0.01+17pt)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{A}};
        \end{tikzonimage}%
    \end{minipage}%
    \begin{minipage}{0.62\textwidth}
        \begin{tikzonimage}[width=0.33\textwidth]
            {figures/crm_amir/profiles-full/fit-comparison.pdf}%
            \node at (0.15, 0.86)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{B}};
        \end{tikzonimage}%
        \begin{tikzonimage}[width=0.33\textwidth]
            {figures/crm_amir/profiles-full/drag force.pdf}%
            \node at (0.15, 0.86)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{C}};
        \end{tikzonimage}%
        \begin{tikzonimage}[width=0.33\textwidth]
            {figures/crm_amir/profiles-full/growth rate.pdf}%
            \node at (0.15, 0.86)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{D}};
        \end{tikzonimage}\\
        \begin{tikzonimage}[width=0.33\textwidth]
            {figures/crm_amir/profiles-full/rod rigidity.pdf}%
            \node at (0.15, 0.86)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{E}};
        \end{tikzonimage}%
        \begin{tikzonimage}[width=0.33\textwidth]
            {figures/crm_amir/profiles-full/spring tension.pdf}%
            \node at (0.15, 0.86)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{F}};
        \end{tikzonimage}%
        \begin{tikzonimage}[width=0.33\textwidth]
            {figures/crm_amir/profiles-full/damping.pdf}%
            \node at (0.15, 0.86)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{G}};
        \end{tikzonimage}%
    \end{minipage}
    \caption{
        Subfigure (A) shows a snapshot of the experiments performed by \cite{Amir2014_2}.
        Division of the bacteria is inhibited and they are trapped within a mother machine such that
        a controlled flow can be exerted on them.
        (B) A comparison of the initial and bent state show good visual agreement of our prediction
        with the experimental data.
        Subfigures (C-G) show likelihood profiles for the individual parameters.
    }
    \label{fig:amir-bending-simulation}
\end{figure}

@@

To show the usefulness of our previously developed methods (see
section~\ref{section:parameter-estimation}), we will use them to estimate the parameters individual
growing \textit{E.Coli} using a sequence of microscopic images.
The data we use~\cite{https://doi.org/10.3203/iwf/k-129} (see
section~\ref{section:data-code-availability}) has been automatically segmented with the
omnipose~\cite{Cutler2022} algorithm which provides us with the necessary cell masks.

% --------------------------------------------------------------------------------------------------
\subsection{Individual Treatment}
We have already suspected (see table~\ref{table:simulation-aspects}) that in order to properly
estimate parameters of our system, we need to treat every cell individually, thus assigning
parameters on a single-cell level.
This means that we increase the total number of parameters that need to be sampled within an
optimization routine.
Given $N_c$ cells and $N_p$ parameters per cell and $N_u$ individual parameters (where
$N_u\leq N_p$), the total amount of parameters to be estimated is

@@

It is clear, that we should avoid to needlessly assign every parameter individually since the volume
of the parameter space that needs to be sampled, scales exponentially with the dimension ie. the
number of parameters.
However, we will now present data that indicate that an individual treatment is in fact necessary.
Figure~\ref{fig:estimated-growth-rates} shows the rod-lengths of individual bacteria which have been
calculated from the extracted positions.
We fit a delayed exponential function to them which is defined by

@@

% --------------------------------------------------------------------------------------------------
\subsection{Without Division}
For now, we will focus on a time-interval which does not contain any division events and at which
the initial lag-phase of our bacteria has already passed.
By doing so, we can utilize the simpler and more performant position comparison scheme for our loss
function.
Furthermore, we need not to estimate the lag-time parameters which improves performance of our
optimization algorithm.
% For this dataset, we assumed that all parameters which specify the interaction potential are
% identical across all agents but growth rates of the cells are individual.
We chose to optimize for the damping of agents' movement within the medium, 3 interaction parameters
of the Mie potential $n,m,V_0$ a single radius $r$ for all agents and growth rates which were chosen
individually for each cell.
We removed any stochastic motion contributions by setting $D=0$.
This leads to a total of $5+1\times 6=11$ variable parameters.
As highlighted before, in order to model non-flexible rods, we set the rigidity and spring tension
of the rod to a high, fixed value.
To estimate these parameters we used the differential evolution~\cite{Storn1997} global optimization
algorithm which was initially seeded with a sample generated by the latin-hypercube~\cite{McKay1979}
method.
Finally, we performed a local minimization using the L-BFGS-B algorithm~\cite{Liu1989}.

Figure~\ref{fig:parameter-estimates-single-step} shows profile-likelihoods for each optimized
parameter with respect to the optimization results.
We can see that all parameters can be estimated by our optimization approach and that no
non-identifiability~\cite{Raue2009} is present.
These plots also show that the individual growth rates of the bacteria can be estimated effectively.

@@

In the next step, we extend our previously used time-series with successive images including
cell division events which means that we now have to use the imaging-based comparison algorithm (see
section~\ref{section:parameter-estimation}).
A practical problem in extending the time series is that the segmentation algorithm was not able to
properly segment the individual bacteria around the division event which meant that we had to omit
parts of the snapshots, leaving us with only incomplete data.

% Since we have already optimized said system, we can reduce the computational demand by choosing the
% parameters which were obtained by our previous attempts and extend them with the parameters that the
% daughter cells will carry.
We optimize for the same parameters as done before.
In addition to assigning growth rates individually, we also need to consider division lengths at
which the bacteria split and the new individual growth rates of the daughter cells as additional
parameters.
Since our simulation involves the division of 4 cells into 8 new ones, in principle, this leads
to a total of $8$ new growth rates and $4$ division lengths.
% But to decrease the size of the parameter space, we assume that the growth rates of the daughter
% cells are identical between every sibling, leaving us at only $4$ new growth rates and a total of
% $8$ parameters.
% Future approaches should aim to loosen this assumption, allowing to optimize every new growth rate.
To optimize this system, we used a similar optimization approach by again seeding with samples
generated via latin-hypercube~\cite{McKay1979}, then applying the differential evolution
algorithm~\cite{Storn1997} and finally a local minimization with Nelder-Mead~\cite{Gao2010}.
We used the value $0.5$ for the parent penalty, which aims to provide a smooth transition between
not accounting for them and assigning full weighting to this difference.
Figure~\ref{fig:celldiffs-progression-with-division} shows the difference between the cell mask as
given by the data and the cell mask predicted by the best fit of our model.
As expected, the fully-optimized system does not produce differences where the parental penalty is
required.
However, its value is frequently used within the the optimization scheme itself.

We can again calculate likelihood profiles for every optimized parameter.
The results displayed in Figure~\ref{fig:likelihood-profiles-comparison-with-division} show that
some curves exhibit a plateau close to the calculated optimum of the estimated parameter.
This concerns the division lengths and some growth rates of the mother bacteria which both determine
if and when a cell divides.
Such behaviour can be attributed to the missing images around the division events of the cells which
were not able to be segmented.
\textbf{TODO check this with data}
It can be argued that this leads to a non-identifiability for the first division length while the
remaining parameters are still identifiable although the effect is also notable.
These results highlight a reassuring finding, namely that the method of profile-likelihood is able
to properly display this lack of data.
It therefore further underlines the accuracy and predictive power of our methods.

The imaging-based comparison algorithm is computationally much more expensive compared to the
simpler position-comparison algorithm.
There are 4 main steps which are executed within any single optimization iteration that contribute
to the total wall time.
These steps are prediction via the computational model ($15.63(21)\%$), mask adjustment of the data
masks ($14.49(19)\%$), mask rendering for the numerical results ($69.2(1.4)\%$) and finally
comparison of the masks ($0.68(5)\%$) (see section \ref{section:supplement-performance}).
The second step alters the masks provided by the data for every individual numerical simulation.
This is required since we need to ensure that the colors of the data-masks match the colors of the
masks produced by our computational model.
To this end, we need to construct a family tree of the data-bacteria and compare with the
\textit{in-silico} family tree.
We can see that the generation of masks from the numerical results takes up the majority of the work.
In addition, the step of mask adjustment would not have been required within the position-comparison
algorithm.
Combining these two values, the position-comparison algorithm is $\approx 6.13(8)$ times faster.

@@

\begin{itemize}
    \item Model does not capture every aspect of rod-shaped bacteria. Needs to extended (see our
        review).
    \begin{enumerate}
        \item polar interactions
        \item differentiation for van Gogh bundles; surfactin-producing, matrix-producing cells.
        \item Proper friction; this might have a huge implication on the estimation of
            parameters~\cite{Grant2014}.
            This paper has already implemented this~\cite{Doumic2020}.
            We can build on top of that.
        \item Extracellular Reactions~\cite{Li2025}
        \item see supplement for full list \ref{table:simulation-aspects-supplement}
    \end{enumerate}
    \item Data Extraction: Skeletonization Algorithm ultimately not good enough for some scenarios
        (i.e. overlapping of cells, endpoints can sometimes be "too short")
    \begin{itemize}
        \item Possibly use AI for new algorithm
    \end{itemize}
    \item Image generation; Produce high-quality near-realistic microscopic images with cell-masks
        from scratch with mechanistic model; train cell-segmentation and more importantly
        cell-tracking algorithms with that.
    \item Lack of data -> this study establishes only methods -> apply it much more broadly in
        future
\end{itemize}

@@

\textbf{Discussion Advanced Optimizations}\\
\begin{itemize}
    \item 
\end{itemize}

@@

\begin{figure}
    \centering
    \begin{tikzonimage}[width=0.33\textwidth]
        {figures/crm_amir/profiles-reduced/fit-comparison.pdf}%
        \node at (0.15, 0.86)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{B}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.33\textwidth]
        {figures/crm_amir/profiles-reduced/drag force.pdf}%
        \node at (0.15, 0.86)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{C}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.33\textwidth]
        {figures/crm_amir/profiles-reduced/growth rate.pdf}%
        \node at (0.15, 0.86)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{D}};
    \end{tikzonimage}\\
    \begin{tikzonimage}[width=0.33\textwidth]
        {figures/crm_amir/profiles-reduced/rod rigidity.pdf}%
        \node at (0.15, 0.86)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{E}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.33\textwidth]
        {figures/crm_amir/profiles-reduced/rigidity to spring tension ratio.pdf}%
        \node at (0.15, 0.86)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{F}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.33\textwidth]
        {figures/crm_amir/profiles-reduced/damping.pdf}%
        \node at (0.15, 0.86)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{G}};
    \end{tikzonimage}%
    \caption{
        \textbf{TODO}
    }
\end{figure}

\subsubsection{With Division}
